---
title: "Insurance factors identification"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## R Project

The data gives the details of third party motor insurance claims in Sweden for the year 1977. In Sweden, all motor insurance companies apply identical risk arguments to classify customers, and thus their portfolios and their claims statistics can be combined. The data were compiled by a Swedish Committee on the Analysis of Risk Premium in Motor Insurance. The Committee was asked to look into the problem of analyzing the real influence on the claims of the risk arguments and to compare this structure with the actual tariff.



```{r}
Insdata <- read.csv("C:\\Users\\HP\\Desktop\\R Projects\\4_Insurance-Analysis-master\\SwedishMotorInsurance.csv")
View(Insdata)

dim(Insdata)

#--------------------------------------------

summary(Insdata)
#--------------------------------------------

cor(Insdata$Claims,Insdata$Payment) #--high +ve correlation

cor(Insdata$Insured,Insdata$Payment) #--high +ve correlation

plot(Insdata$Insured,Insdata$Payment) 

plot(Insdata$Claims,Insdata$Payment) 

#----------------------------------------------

lineModel <- lm(Payment ~ ., data = Insdata)
summary(lineModel)

#----------------------------------------------

ZoneResult <- apply(Insdata[,c(5,6,7)],2, function(x)tapply(x, Insdata$Zone, mean))
ZoneResult

KmResult <- apply(Insdata[,c(5,6,7)],2, function(x)tapply(x, Insdata$Kilometres, mean))
KmResult

BonusResult <- apply(Insdata[,c(5,6,7)],2, function(x)tapply(x, Insdata$Bonus, mean))
BonusResult

#----------------------------------------------------

md <- lm(Insdata$Claims ~ Insdata$Kilometres + Insdata$Zone + Insdata$Bonus + Insdata$Make + Insdata$Insured) 
options(scipen=999)
summary(md)
```
